Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-17 paper/main.tex

    The analysis presented in Fig.~\ref{fig:decomposition} has been repeated for the whole set of simulations, and is reported in Appendix~\ref{sec:gallery_of_gaps} for completeness. From this analysis we can derive a statistical view of: 1) the number of gaps generated on Palomar~5 stream by the whole system of Galactic globular clusters; 2) the clusters which generated these gaps and the time history of these perturbations. From this, we can then quantify: 3) the properties of the perturbers (their masses, sizes and their orbital parameters) as well as 4) the impact geometry of the encounters, which allows us to understand which encounters are more favorable to generate gaps in Palomar~5 stream. In the following, we will present results of this analysis, by starting from addressing points 1) and 2).

>>>>

    The analysis presented in Fig.~\ref{fig:decomposition} has been repeated for the whole set of simulations, and is reported in Appendix~\ref{sec:gallery_of_gaps} for completeness. For all of the streams, morphologically speaking, the only changes appear to be the existence of gaps or not. We do not observe a thickening of the streams due to an increased velocity dispersion.

    From this analysis we can derive a statistical view of: 1) the number of gaps generated on Pal~5 stream by the whole system of Galactic globular clusters; 2) the clusters which generated these gaps and the time history of these perturbations. From this, we can then quantify: 3) the properties of the perturbers (their masses, sizes and their orbital parameters) as well as 4) the impact geometry of the encounters, which allows us to understand which encounters are more favorable to generate gaps in Pal~5 stream. In the following, we will present results of this analysis, by starting from addressing points 1) and 2).
